A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-12 paper.tex
minor

In \cite{ElliottSafronov} we studied the supersymmetric twisting procedure as applied to factorization algebras on $\RR^n$ with an action of a supersymmetry algebra.  If $Q$ is a topological supercharge, then the $Q$-twist $\obs^Q$ of a supersymmetric factorization algebra automatically satisfies a strong translation invariance condition: all translations must act homotopically trivially.  In good circumstances, we can say even more.  An \emph{$\bb E_n$-algebra} is an algebra over the operad of little $n$-disks; in the language above, this is a factorization algebra for which homotopy equivalent configurations $U_1, U_2 \sub V$ induce homotopy equivalent products.
\begin{theorem}[{\cite[Theorem 3]{ElliottSafronov}}]
If $Q$ is a topological supercharge, and the operator $\obs^Q(B_r(0)) \to \obs^Q(B_R(0))$ associated to the inclusion of concentric balls is an equivalence, then the factorization algebra $\obs^Q$ has the canonical structure of an $\bb E_n$-algebra.
\end{theorem}
The hypothesis of the theorem is automatically satisfied, for example, for superconformal theories, and should be concretely checkable in examples.

@@

\textbf{Dimension 7}
\begin{itemize}
 \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang-Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.  The minimal twist is equivalent to a generalized version of BF theory with one topological direction and three complex holomorphic directions.  This theory is $\mr U(3)$-invariant, and can be defined on the product of a complex 3-fold with a flat 1-manifold.
 \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in three directions and holomorphic in the remaining two complex directions.  This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory.  It is $\SU(2) \times \Spin(3;\RR)$-invariant, and can be defined on the product of a Calabi-Yau surface and a 3-manifold with spin structure.
 \item \emph{$\mc N=1$ topological twist.} The topological twist in 8-dimensions reduces to a topological twist in 7 dimensions.  This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the minimal twist.  It is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.  This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the $G_2$-monopole equations.
\end{itemize}

\textbf{Dimension 6}
\begin{itemize}
 \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} There is a holomorphic twist in 6 dimensions that can be defined for the $\mc N=(1,0)$ supersymmetric theory coupled to a hypermultiplet valued in a symplectic representation $U$.  This twist is equivalent to holomorphic Chern-Simons theory coupled to a holomorphic symplectic boson valued in the representation $U$.  It is generally only $\ZZ/2\ZZ$-graded, but can be promoted to a $\ZZ$-graded theory when $U = T^*R$ is of cotangent type.  It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and the metalinear unitary group $\mr {MU}(3)$ in the cotangent case, and can be defined on complex 3-folds with a choice of square root of the canonical bundle.  When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter.  This twist has also been calculated in forthcoming work of Dylan Butson \cite{Butson}. 
 \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.  The one by a supercharge of rank $(1,1)$ is equivalent to a generalized form of BF theory, with two topological directions and two complex holomorphic directions.  This theory is $\mr U(2) \times \spin(2;\RR)$-invariant, and can be defined on the product of a complex surface with a Riemann surface.
 \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.} The other intermediate twist, by a rank $(2,2)$ supercharge, is equivalent to a generalized form of Chern-Simons theory with four real directions and one complex holomorphic direction.  This theory is only $\ZZ/2\ZZ$-graded.  It is invariant for the action of $\spin(4;\RR)$, and can be defined on the product of a flat Riemann surface and a spin 4-manifold.
 \item \emph{$\mc N=(1,1)$ topological twist.} Finally, there is a topological twist in 6 dimensions obtained by dimensionally reducing the 7-dimensional topological twist.  This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the holomorphic twist.  It is $\SU(3)$-invariant, although the full one-parameter family is only $\SU(2) \times \spin(2;\RR)$-invariant.  This theory was also studied in \cite{AcharyaOLoughlinSpence}; its equations of motion include the Donaldson-Thomas equations.
\end{itemize}

>>>>

In \cite{ElliottSafronov} we studied the supersymmetric twisting procedure as applied to factorization algebras on $\RR^n$ with an action of a supersymmetry algebra.  If $Q$ is a topological supercharge, then the $Q$-twist $\obs^Q$ of a supersymmetric factorization algebra automatically satisfies a strong translation invariance condition: all translations must act homotopically trivially.  In good circumstances, we can say even more.  An \emph{$\bb E_n$-algebra} is an algebra over the operad of little $n$-disks; in the language above, this is a factorization algebra for which homotopy equivalent configurations $U_1, U_2 \sub V$ induce homotopy equivalent products.
\begin{nonum}[{\cite[Theorem 3]{ElliottSafronov}}]
If $Q$ is a topological supercharge, and the operator $\obs^Q(B_r(0)) \to \obs^Q(B_R(0))$ associated to the inclusion of concentric balls is an equivalence, then the factorization algebra $\obs^Q$ has the canonical structure of an $\bb E_n$-algebra.
\end{nonum}
The hypothesis of the theorem is automatically satisfied, for example, for superconformal theories, and should be concretely checkable in examples.

@@

\textbf{Dimension 7}
\begin{itemize}
 \item \emph{$\mc N=1$ minimal twist.} The twists of super Yang-Mills theory in 7 dimensions arise by dimensionally reducing the twists in 8 dimensions.  The minimal twist is equivalent to a generalized version of BF theory with one topological direction and three complex holomorphic directions.  This theory is $\mr U(3)$-invariant, and can be defined on the product of a complex 3-fold with a flat 1-manifold.
 \item \emph{$\mc N=1$ intermediate twist.} This minimal twist admits a further twist which is topological in three directions and holomorphic in the remaining two complex directions.  This intermediate twisted theory is equivalent, as a $\ZZ/2\ZZ$-graded theory, to a generalized version of Chern-Simons theory.  It is $\SU(2) \times \Spin(3;\RR)$-invariant, and can be defined on the product of a Calabi-Yau surface and a 3-manifold with spin structure.
 \item \emph{$\mc N=1$ topological twist.} The topological twist in 8-dimensions reduces to a topological twist in 7 dimensions.  This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the minimal twist.  It is $G_2$-invariant, although the full one-parameter family is only $\SU(3)$-invariant.  This theory was also studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}; its equations of motion include the $G_2$-monopole equations.
\end{itemize}

\textbf{Dimension 6}
\begin{itemize}
 \item \emph{$\mc N=(1,0)$ and $\mc N=(1,1)$ holomorphic twist.} There is a holomorphic twist in 6 dimensions that can be defined for the $\mc N=(1,0)$ supersymmetric theory coupled to a hypermultiplet valued in a symplectic representation $U$.  This twist is equivalent to holomorphic Chern-Simons theory coupled to a holomorphic symplectic boson valued in the representation $U$.  It is generally only $\ZZ/2\ZZ$-graded, but can be promoted to a $\ZZ$-graded theory when $U = T^*R$ is of cotangent type.  It is invariant for the action of $\SU(3)$ in general, and can be defined on Calabi-Yau 3-folds, and the metalinear unitary group $\mr {MU}(3)$ in the cotangent case, and can be defined on complex 3-folds with a choice of square root of the canonical bundle.  When $U = T^*\gg$, the supersymmetry can be promoted to $\mc N=(1,1)$ supersymmetry, and the twist can be identified with a holomorphic BF theory coupled to adjoint holomorphic matter.  This twist has also been calculated in forthcoming work of Dylan Butson \cite{Butson}. 
 \item \emph{$\mc N=(1,1)$ special rank $(1,1)$ twist.} In the $\mc N=(1,1)$ case there are two intermediate twists.  The one by a supercharge of rank $(1,1)$ is equivalent to a generalized form of BF theory, with two topological directions and two complex holomorphic directions.  This theory is $\mr U(2) \times \spin(2;\RR)$-invariant, and can be defined on the product of a complex surface with a Riemann surface.
 \item \emph{$\mc N=(1,1)$ rank $(2,2)$ twist.} The other intermediate twist, by a rank $(2,2)$ supercharge, is equivalent to a generalized form of Chern-Simons theory with four real directions and one complex holomorphic direction.  This theory is only $\ZZ/2\ZZ$-graded.  It is invariant for the action of $\spin(4;\RR)$, and can be defined on the product of a flat Riemann surface and a spin 4-manifold.
 \item \emph{$\mc N=(1,1)$ topological twist.} Finally, there is a topological twist in 6 dimensions obtained by dimensionally reducing the 7-dimensional topological twist.  This theory is again perturbatively trivial, but can be realized as the generic point in a 1-parameter degeneration of the holomorphic twist.  It is $\SU(3)$-invariant, although the full one-parameter family is only $\SU(2) \times \spin(2;\RR)$-invariant.  This theory was also studied in \cite{AcharyaOLoughlinSpence, BaulieuKannoSinger}; its equations of motion include the Donaldson-Thomas equations.
\end{itemize}
